Model LF

### 2022-11-03 max_dp endogen stød.Rmd
Commit

```{r}
plot((yk_ds_s2_up / yk_ds_sbs2_up), col= "red", main= "% Change in Net exports");
lines((yk_ds_s2_low / yk_ds_sbs2_low), col="black");
lines((yk_ds_02 / yk_ds_bs2), col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

```{r}
plot((unemp_s2_up - unemp_sbs2_up)*1000, col= "red", main= "Change in Unemployment (people)");
lines((unemp_s2_low - unemp_sbs2_low)*1000, col="black");
lines((unemp_02 - unemp_bs2)*1000, col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

## Sens 3_low

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1), main= "% Change in Productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.26"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((yk_ds_s3_low/yk_ds_sbs3_low), col= "red", ylim= c(min(yk_ds_s3_low/yk_ds_sbs3_low), max(yk_ds_03/yk_ds_bs3)), main= "% Change in GDP");
lines((yk_ds_03/yk_ds_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.26"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s3_low-inflation_sbs3_low), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_03-inflation_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.2"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

Udvikling i Employment med estimat = 0.1:

```{r}
plot((unemp_s3_low-unemp_sbs3_low)*1000, col= "red", ylab= "Change in employment (people)", main= "Employed estimate set to 0.1"); grid()
```

```{r}
plot((nl_g_s3_low-nl_g_sbs3_low), col= "red", ylab= "Change in Gov (people)", main= "Government net-lednings estimate set to 0.1"); grid()
```

>>>>

```{r}
plot((yk_ds_s2_up / yk_ds_sbs2_up), col= "red", ylab= "% Change inm GDP", main= "Sensitivity of GDP");
lines((yk_ds_s2_low / yk_ds_sbs2_low), col="black");
lines((yk_ds_02 / yk_ds_bs2), col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

```{r}
plot((unemp_s2_up - unemp_sbs2_up)*1000, col= "red", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s2_low - unemp_sbs2_low)*1000, col="black");
lines((unemp_02 - unemp_bs2)*1000, col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

## Sens 3

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(1, 1.01), ylab= "% Change in Productivity", main= "Sensitivity of productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.03 and 0.5",
                       "Estimate is 0.6 and 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((yk_ds_s3_low/yk_ds_sbs3_low), col= "red", ylab= "% Change in GDP", main= "Sensitivity of GDP");
lines((yk_ds_03/yk_ds_bs3), col="black");
legend("top", legend=c("Estimate set to 0.03 and 0.5",
                       "Estimate is 0.6 and 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((unemp_s3_low-unemp_sbs3_low)*1000, col= "red", ylim= c(0,25000), ylab= "% Change in Unemployment", main= "Sensitivity of unemployment");
lines((unemp_03-unemp_bs3)*1000, col="black");
legend("top", legend=c("Estimate set to 0.03 and 0.5",
                       "Estimate is 0.6 and 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```
